---
framework: bootstrap
output: html_document
highlighter: prettify
hitheme: twitter-bootstrap
mode: selfcontained
github:
branch: gh-pages
user: RohitDhankar
---

<h1 style = "font-size: 72px;line-height: 72px;color: #0b62a4;margin: 20px 0 20px 0;text-shadow: 1px 1px 5px #789;"> Rohit <a href = "https://github.com/RohitDhankar"> GitHub</a>
<br/>
Statistical Quality Control (SQC) using "R"
<br/>
</h1>

<p>

<br/>
1. 99.73% observations to be between +(-)3 Sigma / Six Sigma . 
<br/>
2. Control Charts - UCL , Central Line and LCL , leads to outlier or Special cause detection.
<br/>
3. Using package - "qcc" to create a Control Chart within "R"
<br/>
4. Multivariate Control Charts - Control Ellipsoid - http://arxiv.org/ftp/arxiv/papers/0901/0901.2880.pdf
<br/>

Copyright is of the Authors
Authors:  Edgar Santos-Fernández, Michele Scagliarini -- https://sites.google.com/site/edgarsantosfernandez/home
</P>

```{r results='asis', error=F, warning=F, message=F, tidy = F}

library(MSQC)
library("MSQC", lib.loc="~/R/win-library/3.1")
data(package="MSQC")
library(qcc)
citation("qcc")
#Scrucca, L. (2004). qcc: an R package for quality control
#charting and statistical process control. R News 4/1, 11-17.
set.seed(20)

x <-round(rnorm(120,20,2),2)
length <-matrix(x, ncol=4, byrow=TRUE)
par(mfrow=c(1,2))
qcc(length, type="xbar", std.dev="RMSDF"); qcc(length, type="R")
#
cap<-qcc(length, type="xbar", nsigmas=3, plot=T)
process.capability(cap, spec.limits=c(14,26))
#

mu <-c(0,0) # The Mean vector - "mu" of a Bivariate Normal Distribution 
sigma <- matrix(c(10,3,3,6),2,2) # Sigma the Covariance Matrix 
# The Square Covariance Matrix structure needs to be seen and understood ... 
sigma
#
sigma[1,1]
# Which is the Observation "10" t location - Row - 1 and Column -1, within the Square Matrix "sigma"
sigma[2,2]
# Which is the Observation "6" at location - Row - 2 and Column -2 , within the Square Matrix "sigma"
#
rho <- sigma[1,2]/(sqrt(sigma[1,1]*sigma[2,2])) 
rho
# rho=3/(sqrt(10*6))
# dummy<-3/sqrt(60) - same as value of "rho"
# https://stat.ethz.ch/R-manual/R-devel/library/stats/html/cor.html
#
var1<-seq(-12,12,.7)
var1
#
var2<-var1
knitr::kable(var2)
```

```{r,results='asis',echo=FALSE}

```


```{r results='asis', error=F, warning=F, message=F, tidy = F}
# 
f<-matrix(0, length(var1), length(var1))
for(i in 1:length(var1))
  {
for(j in 1:length(var1))
  {
  f[i,j]<-1/(2*pi*sqrt(sigma[1,1]*sigma[2,2]*(1-rho^2)))*exp(-1/(2*(1-rho^2)) * ((var1[i]-mu[1])^2/sigma[1,1] + (var2[j] - mu[2])^2/sigma[2,2]-2 *rho*((var1[i] - mu[1])*(var2[j]-mu[2]))/(sqrt(sigma[1,1])*sqrt(sigma[2,2]))))}}    

# 
str(f)
#
persp(var1,var2,f,xlab="Var-1",ylab="Var-2",zlab="f(var1,var2)", 
      theta=30,phi=30,col = "red",shade = 0.05,r=50,d=0.02,expand=0.9,ltheta=90,lphi=180, nticks=4,box=F)
#
jet.colors <- colorRampPalette( c("blue", "green") )
#
nbcol <- 100
color <- jet.colors(nbcol)
persp(var1,var2,f,xlab="Var-1",ylab="Var-2",zlab="f(var1,var2)", 
      theta=30,phi=30,col = color,shade = 0.05,r=50,d=0.02,expand=0.9,ltheta=90,lphi=180, nticks=4,box=T)
# Further Shading - using Code from help -persp {graphics}
z <- outer(var1, var2, function(a, b) a*b^2)
nrz <- nrow(z)
ncz <- ncol(z)
# Compute the z-value at the facet centres
zfacet <- z[-1, -1] + z[-1, -ncz] + z[-nrz, -1] + z[-nrz, -ncz]
# Recode facet z-values into color indices
facetcol <- cut(zfacet, nbcol)

persp(var1,var2,f,xlab="Var-1",ylab="Var-2",zlab="f(var1,var2)", 
      theta=30,phi=30,col = color[facetcol],shade = 0.05,r=50,d=0.02,expand=0.9,ltheta=90,lphi=180, nticks=4,box=F)
# In the Above seen Perspective Plot - persp {graphics}
# f == the matrix containing values to be plotted.

```

```{r,results='asis',echo=FALSE}
# R Graphs 

```

<br/>
## Contact...
- [ email](https://github.com/RohitDhankar)
- [ Github ](https://github.com/RohitDhankar)
- [ LinkedIn ](https://www.linkedin.com/in/rohitdhankar )
- [ Twitter  ](https://twitter.com/DhankarRohit)

<br/>
## License - GPL - No Copyright (http://www.gnu.org/licenses/licenses.en.html#GPL)
```

```
[ Rohit Dhankar 2015](https://github.com/RohitDhankar)
